Calculating life expectancy and exploring missingness

### 2017-04-06 Code/1_Explore_Data.Rmd

dat$RID <- paste(dat$stabbrs, dat$year, substr(dat$sex, 1, 1),
                 substr(dat$race, 1, 1), dat$age.n, dat$COD, sep = ".")
```

>>>>

dat$COD.abbrev <- "CAR"
dat$COD.abbrev[dat$COD == "Cancers"] <- "CAN"
dat$COD.abbrev[dat$COD == "Communicable"] <- "CDS"
dat$COD.abbrev[dat$COD == "Non-communicable"] <- "NDS"
dat$COD.abbrev[dat$COD == "Injuries"] <- "INJ"
dat$COD.abbrev[dat$COD == "All other causes"] <- "AOC"

dat$RID <- paste0(dat$stabbrs, dat$year, substr(dat$sex, 1, 1),
                 substr(dat$race, 1, 1), dat$age.n, dat$COD.abbrev)
```
